Data Management for LSST Special Programs

### 2023-10-18 sec_proc.tex
rm subsubsubsection command

\subsubsubsection{Potential issues with Prompt processing for untiled sequences from Special Programs.}

There are two potential issues with Prompt processing for DDFs, or any mini-survey 
that obtains a sequence of untiled images: images at the same pointing or which overlap.
For example, a DDF which obtains a hour-long series of about a hundred images at the same coordinates,
every few nights for a few months.

>>>>

\textbf{Potential issues with Prompt processing for untiled sequences from Special Programs.}
There are two potential issues with Prompt processing for DDFs, or any mini-survey 
that obtains a sequence of untiled images: images at the same pointing or which overlap.
For example, a DDF which obtains a hour-long series of about a hundred images at the same coordinates,
every few nights for a few months.
